---
title: "Wollongong Map"
author: "Mitchell Stares"
date: "5 February 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

```{R}
library(osmdata)
library(sf)
library(tidyverse)
library(leaflet)
```

# Data

Read in geoscience australias boundary layer and limit to NSW
```{r}
nsw_coast <- st_read(dsn = "E:/Coding Tutorials-Learning/NSW_bushfire_mapping/vegetationnswextantnativevegetationv2",
                     layer = "cstauscd_r")
nsw_coast <- filter(nsw_coast, FEAT_CODE == "mainland" & STATE_CODE == 3) #filter the australian wide map to NSW
```

# OSM Queries

```{r}
# osmdata::available_features()
# osmdata::available_tags("boundary")

streets <- getbb("Wollongong Australia")%>%
  opq()%>%
  add_osm_feature(key = "highway", 
                  value = c("motorway", "primary", 
                            "secondary", "tertiary")) %>%
  osmdata_sf()

small_streets <- getbb("Wollongong Australia")%>%
  opq()%>%
  add_osm_feature(key = "highway", 
                  value = c("residential", "living_street",
                            "unclassified",
                            "service", "footway")) %>%
  osmdata_sf()

# country <- getbb("Wollongong Australia") %>%
#   opq() %>%
#   add_osm_feature(key = "boundary",
#                   value = c("aboriginal_lands", "administrative",
#                             "historic", "marker",
#                             "postal_code", "protected_area")) %>%
#   osmdata_sf()
# 
# 
# rivers <- getbb("Wollongong Australia")%>%
#   opq()%>%
#   add_osm_feature(key = "waterway", value = "river") %>%
#   osmdata_sf()

```

# Plot OSM data

This is pretty basic plotting for now. Some of the extra crap I did in powerpoint. 
```{r}

ggplot() +
  geom_sf(data = streets$osm_lines,
          inherit.aes = FALSE,
          color = "#7fc0ff",
          size = .4,
          alpha = .8) +
  geom_sf(data = small_streets$osm_lines,
          inherit.aes = FALSE,
          color = "#ffbe7f",
          size = .4,
          alpha = .6) +
  # geom_sf(data = rivers$osm_lines,
  #         inherit.aes= FALSE,
  #         color = "steelblue",
  #         size = .4,
  #         alpha = .6)+
  geom_sf(data = nsw_coast,
          inherit.aes = FALSE,
          color = "#f0831a",
          size = .4,
          alpha = .8)+
  coord_sf(xlim = c(150.97893, 150.80727),
           ylim = c(-34.35914, -34.49646),
           expand = FALSE) +
 theme_void()+
  theme(
    plot.background = element_rect(fill = "#282828"))


#ggsave("map.png", width = 6, height = 6)
```


# Leaflet "plugin" for boundary box

This leaflet function will throw alerts of the current boundary box of the viewer. Quick and dirty way of finding the boundary box
The alert button will read out the current display box (best to remove width and height for that), where as the function below will allow the bbox as an R variable. 
```{r}
m <- leaflet(width = 500, height= 400) %>% 
  addTiles()  %>% 
  setView(lng = 150.8931, lat = -34.4278, zoom = 12) %>%
  addEasyButton(easyButton(
  states = list(
    easyButtonState(
      stateName="unfrozen-markers",
      icon="ion-toggle",
      title="Get Bounding box",
      onClick = JS("
                     function(btn, map) {
                         alert(map.getBounds().getEast());
                         alert(map.getBounds().getWest());
                         alert(map.getBounds().getNorth());
                         alert(map.getBounds().getSouth());
                         }")
          )
            )
            )
            )

m

getBox <- function(m){
  view <- m$x$setView
  lat <- view[[1]][1]
  lng <- view[[1]][2]
  zoom <- view[[2]]
  zoom_width <- 360 / 2^zoom
  lng_width <- m$width / 256 * zoom_width
  lat_height <- m$height / 256 * zoom_width
  return(c(lng - lng_width/2, lng + lng_width/2, lat - lat_height/2, lat + lat_height/2))
}
getBox(m)

```
